Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-27 demystify.tex
updates

\section{Standard Tests (GREs, IELTS, etc), Work Experiences, Online Courses, and Certificates}\label{sec:standard-tests}

\paragraph{GRE} Most good CS PhD programs in the US (e.g., R1 universities) \textbf{no longer require GREs}, so you don't need to take them.

\textbf{Advice}: In general, don't waste time on the GRE.  However, if you took it and have good scores then you can include and talk about them in your application (but don't expect them to make much difference). But if your scores are bad, then you should not include them in your application, which can be a \red{red flag}.

@@

\begin{commentbox}[Vu:]
  The minimum for GMU (being above this might not mean much, but below is a \red{red flag}).
  \begin{itemize}
    \item GPA: $\ge 3.0$ in your undergrad (but we also consider the rank/prestige of your school)
    \item GRE: not required, though it can help boost your profile
    % \item but if you want to use it, then we expect a total (V+Q) of $\ge 311$ (with a $\ge 157$ Q) and A $\ge 3.0-3.5$.
    \item English requirement tests (one of the below)
          \begin{itemize}
            \item TOEFL: 88 pts in total AND $\ge 20$ points in each subsection OR
            \item IELTS: $\ge 6.5$ OR
            \item DuoLingo Graduate English: $\ge 120$ OR
            \item Pearson Test of Academic English: $\ge 67$
          \end{itemize}
  \end{itemize}
\end{commentbox}

>>>>

\section{Standard Tests (GRE, IELTS, etc), Work Experiences, Online Courses, and Certificates}\label{sec:standard-tests}

\paragraph{GRE} While a few schools still require taking the GRE (e.g., UCF), most good CS PhD programs in the US \textbf{no longer} require it.

\textbf{Advice}: If you haven't taken the GRE or have bad scores, then don't waste time (re)taking it.  However, if you took it and have really good scores then you can include and talk about them in your application (but don't expect them to make much difference). But if your scores are bad, then you should not include them in your application, which can be a \red{red flag}.

@@

\begin{commentbox}[Vu:]
  The minimum for GMU (being above this might not mean much, but below is a \red{red flag}).
  \begin{itemize}
    \item GPA: $\ge 3.0$ in your undergrad (but we also consider the rank/prestige of your school)
    \item GRE: not required
    % \item but if you want to use it, then we expect a total (V+Q) of $\ge 311$ (with a $\ge 157$ Q) and A $\ge 3.0-3.5$.
    \item English requirement tests (one of the below)
          \begin{itemize}
            \item TOEFL: 88 pts in total AND $\ge 20$ points in each subsection OR
            \item IELTS: $\ge 6.5$ OR
            \item DuoLingo Graduate English: $\ge 120$ OR
            \item Pearson Test of Academic English: $\ge 67$
          \end{itemize}
  \end{itemize}
\end{commentbox}
